The title

### 2023-03-28 doc/multiverse.Rmd

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location", "pa_mostactivehr"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location", "Pa_mostactivehr")
)
moderator_df$moderator_sentence <- stringr::str_to_sentence(moderator_df$moderator)

>>>>

moderator_df <- data.frame(
  moderator = c("bmi", "ses", "sex", "weekday", "season", "region", "daylight", "wear_location", "pa_mostactivehr"),
  moderator_formal = c("BMI", "SES", "sex", "weekday", "season", "region", "daylight hours", "wear location", "most active hour"),
  image_path = c("Bmi", "Ses", "Sex", "Weekday_x", "Season", "Region", "Daylight_hours", "Accelerometer_wear_location", "Pa_mostactivehr")
)
